Differential Expression - HBCC - dsACC - Sex

### 2020-08-01 individual-cohorts/HBCC_DLPFC_DE.Rmd
Test Sex with Dx added to the model

# Set covariates to adjust for from model selection
adjust.covars <- c("Sex", "ageOfDeath", "RIN", "IntronicRate", "IntragenicRate", "IntergenicRate")
```

>>>>

# Set covariates to adjust for from model selection
adjust.covars <- c("Sex", "Dx", "ageOfDeath", "RIN", "IntronicRate", "IntragenicRate", "IntergenicRate")
```

### 2020-08-01 individual-cohorts/HBCC_dsACC_DE.Rmd
Test Sex with Dx added to the model

# Set covariates to adjust for from model selection
adjust.covars <- c("Sex", "RIN", "IntronicRate", "IntragenicRate", "IntergenicRate", "ageOfDeath")
random_effect <- c("IsolationBatch")
```

>>>>

# Set covariates to adjust for from model selection
adjust.covars <- c("Sex", "Dx", "RIN", "IntronicRate", "IntragenicRate", "IntergenicRate", "ageOfDeath")
random_effect <- c("IsolationBatch")
```
